### 2024-06-19 basic-statistics.qmd
20240619 - typo
20240619 - regression framework

1. We (correctly) reject the null hypothesis when it is in fact false ($1 - \beta$).
This is a true positive.
For instance, we may correctly determine that Quarterbacks have longer careers than Running Backs.
1. We (correctly) fail to reject the null hypothesis when it is in fact true ($1 - \alpha$).
This is a true negative.
For instance, we may correctly determine that Quarterbacks do not have longer careers than Running Backs.
1. We (incorrectly) reject the null hypothesis when it is in fact true ($\alpha$).
This is a false positive.
When performing null hypothesis testing, a false positive is known as a Type I error.
For instance, we may incorrectly determine that Quarterbacks have longer careers than Running Backs when, in fact, Quarterbacks and Running Backs do not differ in their career length.
1. We (incorrectly) fail to reject the null hypothesis when it is in fact false ($\beta$).
This is a false positive.
When performing null hypothesis testing, a false negative is known as a Type II error.
For instance, we may incorrectly determine that Quarterbacks and Running Backs do not differ in their career length when, in fact, Quarterbacks have longer careers than Running Backs.

@@

>>>>

1. We (correctly) reject the null hypothesis when it is in fact false ($1 - \beta$).
This is a true positive.
For instance, we may correctly determine that Quarterbacks have longer careers than Running Backs.
1. We (correctly) fail to reject the null hypothesis when it is in fact true ($1 - \alpha$).
This is a true negative.
For instance, we may correctly determine that Quarterbacks do not have longer careers than Running Backs.
1. We (incorrectly) reject the null hypothesis when it is in fact true ($\alpha$).
This is a false positive.
When performing null hypothesis testing, a false positive is known as a Type I error.
For instance, we may incorrectly determine that Quarterbacks have longer careers than Running Backs when, in fact, Quarterbacks and Running Backs do not differ in their career length.
1. We (incorrectly) fail to reject the null hypothesis when it is in fact false ($\beta$).
This is a false negative.
When performing null hypothesis testing, a false negative is known as a Type II error.
For instance, we may incorrectly determine that Quarterbacks and Running Backs do not differ in their career length when, in fact, Quarterbacks have longer careers than Running Backs.

@@

However, many statistical tests can be re-formulated in a regression framework, as in @fig-statisticalDecisionTreeRegression.

::: {#fig-statisticalDecisionTreeRegression}
![](images/statisticalDecisionTreeRegression.png)

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure, Re-Formulated in a Regression Framework. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including re-formulating the tests in a regression framework.
:::
